---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. 
Please edit that file and run `just render` -->

# cox-ipw

This is the code and configuration for `cox-ipw`, which is an R reusable action for the OpenSAFELY framework.

The action:

- Samples data and applies inverse probability weights
- Performs survival data setup
- Checks covariate variation
- Fits the specified Cox model

## Usage

### Options

The available options for the action can be specified using the flags style (i.e., `--argname=argvalue`) or the config style (i.e., `config: argname: argvalue`).
The available options (using the flags style) are as follows:

```{r, include=FALSE}
# Taken from
# https://github.com/yihui/knitr-examples/blob/master/077-wrap-output.Rmd
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x <- knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x <- strwrap(x, width = n)
    x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})
```
```{r, echo=FALSE, comment = '', linewidth=80}
source_lines <- function(file, lines) {
    source(textConnection(readLines(file)[lines]))
}
# Note: in the following command the last line should be the line that
# creates the opt_parser object using OptionParser(...)
source_lines("analysis/cox-ipw.R", 1:185)
optparse::print_help(opt_parser)
```

### Action with options set to default

The action can be specified in the `project.yaml` with its options at their default values as follows, 
where you should replace `[version]` with the latest tag from 
[here](https://github.com/opensafely-actions/cox-ipw/tags), e.g., `v0.0.1`. 
Note that no space is allowed between `cox-ipw:` and `[version]`.

```yaml
cox_ipw:
  run: cox-ipw:[version]
  needs:
  - generate-dataset
  outputs:
    moderately_sensitive:
      arguments: output/args-results.csv
      estimates: output/results.csv
```

### Action with options specified as arguments

The action ccan be specified in the `project.yaml` with its options specified as arguments as follows, 
where you should replace `[version]` with the latest tag from 
[here](https://github.com/opensafely-actions/cox-ipw/tags), e.g., `v0.0.1`. 
Note in YAML `>` indicates that the subsequent nested lines should be treated as a single line.

```yaml
cox_ipw:
  run: >
    cox-ipw:[version]
      --df_output=results.csv
  needs:
  - generate-dataset
  outputs:
    moderately_sensitive:
      arguments: output/args-results.csv
      estimates: output/results.csv
```

### Actions with options specified using config

The action can be specified in the `project.yaml` with its options specified  using a `config:` key in the YAML as follows, 
where you should replace `[version]` with the latest tag from 
[here](https://github.com/opensafely-actions/cox-ipw/tags), e.g., `v0.0.1`. 
Note that options specified in the config overwrite those specified at the command line.

```yaml
  cox_ipw:
    run: cox-ipw:[version]
    config:
      df_output: results.csv
    needs:
    - generate-dataset
    outputs:
      moderately_sensitive:
        arguments: output/args-results.csv
        estimates: output/results.csv
```

### Recording of options

A csv file of argument values is automatically named with
`args-` prepended to the name of the output data csv file. Hence, both
the output data file and the file of argument values should be listed as
`moderately_sensitive` outputs as shown in the above example.

## Notes for developers

Please see [_DEVELOPERS.md_](DEVELOPERS.md).

For more information about reusable actions see [here](https://docs.opensafely.org/actions-reusable/).

# About the OpenSAFELY framework

The OpenSAFELY framework is a Trusted Research Environment (TRE) for electronic
health records research in the NHS, with a focus on public accountability and
research quality.

Read more at [OpenSAFELY.org](https://opensafely.org).

# Licences
As standard, research projects have a MIT license.
