---
output: github_document
---

<!-- README.md is generated from README.Rmd. 
Please edit that file and rerun in R `rmarkdown::render('README.Rmd')` -->

# cox-ipw

This is the code and configuration for `cox-ipw`, which is an R reusable action for the OpenSAFELY framework.

The action:

- Samples data and applies inverse probability weights
- Performs survival data setup
- Checks covariate variation
- Fits the specified Cox model

## Usage

The arguments to the action are specified using the flags style (i.e., `--argname=argvalue`), the arguments are as follows.

```{r, include=FALSE}
# Taken from
# https://github.com/yihui/knitr-examples/blob/master/077-wrap-output.Rmd
library(knitr)
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```
```{r, echo=FALSE, comment = '', linewidth=80}
source_lines <- function(file, lines){
    source(textConnection(readLines(file)[lines]))
}
# Note: in the following command the last line, 56, should be the line that
# creates the opt_parser object using OptionParser(...)
source_lines("analysis/cox-ipw.R", 1:58)
optparse::print_help(opt_parser)
```

This action can be specified in the `project.yaml` with its default values as follows.

```yaml
my_cox_ipw:
  run: cox-ipw:
```

This action can be run specifying arguments as follows 
(in YAML `>` indicates to treat the subsequent nested lines as a single line).

```yaml
my_cox_ipw:
  run: >
    cox-ipw: 
      --df_input=other_input_file.csv
      --df_output=other_output_file.csv
```

## Notes for developers

Please see [_DEVELOPERS.md_](DEVELOPERS.md).

For more information about reusable actions see [here](https://docs.opensafely.org/actions-reusable/).

# About the OpenSAFELY framework

The OpenSAFELY framework is a Trusted Research Environment (TRE) for electronic
health records research in the NHS, with a focus on public accountability and
research quality.

Read more at [OpenSAFELY.org](https://opensafely.org).

# Licences
As standard, research projects have a MIT license. 
